\chapter{Objective}
\begin{enumerate}
  \item \textbf{Primary Objective} The primary objective of this report is to complete my mandatory internship program as a graduate student at the faculty of  Electrical Engineering and Information Technology RWTH Aachen University. As an attendee of this master's degree program, every student is required to complete a mandatory internship in the industry for at least 16 weeks. Being a student who mostly took most of the courses of Lehrstuhl und Institut für Vernetzte Systeme and Lehrstuhl für Radar-Systemtechnik, I always wanted to gain practical knowledge about the state of art communication cellular technology. This internship at Qualcomm CDMA Technologies GmbH. for the tenure of six months has enlightened me with that exposure mostly on the user equipment side as a 4G and NR5G modem testing intern.
  \item \textbf{Secondary Objectives}
        \begin{itemize}
            \item To have an overview of LTE, LTE-Advanced and NR5G air interfaces.
            \item To know the basic Target testing procedure on all the modem peripheral subsystem software owned by Qualcomm.
            \item To know and operate all the tools internally developed by Qualcomm for the testing line of the 4G and 5G modem systems.
            \item To be responsible for a certain number of testing platforms of the modem testing line and reporting (tool-specific issues) and debugging issues while configuring devices for particular test cases.
            \item To know automation of the Qualcomm's internal tools with Batch and Perl scripting to efficiently configure multiple devices in parallel.
            \item To fetch the log packets for the selected RAT with an internal tool in the lab and out in the field with a particular band combination.
            \item To do log packet analysis for the sanity check of RAT with certain band combinations and threshold RSRP and RSRQ at a certain location in the field
        \end{itemize}
    \item \textbf{Methodology of the report} The nature of work requires a thorough knowledge of the architectures, internal tool suite developed, and the processing flow of the testing framework of the modem chipset along with the overview of NR5G and LTE RATs.
        \begin{itemize}
            \item \textbf{Primary sources}
                   \begin{itemize}
                       \item Two weeks training period for the task assigned by the colleagues
                       \item Qualcomm's internal training program on LTE and NR5G
                       \item Supervised task session for one week by the colleague assigned for training.
                       \item Qualcomm's internal wiki.
                       \item Daily automated execution of test cases in target tests with scripting and tool suits.
                   \end{itemize}
               \item \textbf{Secondary sources} 
                    \begin{itemize}
                        \item Weekly meetings to sharpen the log analysis skills and testing optimization further.
                        \item Daily Session reports by the test technicians for the better test execution understanding
                        \item Tool manual released by the Qualcomm's internal tool developers.
                    \end{itemize}
        \end{itemize}
    \item \textbf{Limitation of the report} The primary limitation of preparing this report is explaining information without disclosing sensitive information or data that might affect their business. 
    To abide by this, I am obliged to not use the internal target names in this report.
\end{enumerate}